\documentclass{article}
\usepackage{blindtext}
\usepackage{titlesec}
\usepackage{xcolor}
\title{Literature Review Structure}
\author{Rowan Adeya}
\date{ }
\begin{document}

\maketitle

\tableofcontents

\newpage

\section{Quantum Resources in Two-Level Systems Coupled to Quantum Harmonic Oscillators}

\section{Introduction}

\begin{enumerate}
    \item \textbf{PURPOSE:} aim is to write a small article for a physics education journal. The purpose will be to give a \textbf{general overview} of the TLS-HO model, quantum resources, and the quantum resources in the TLS-HO model.
    \item \textbf{MOTIVATION:} motivation?
    \item \textbf{FOCUS:} In this paper, we shall be taking a look at Coherence and Entanglement in Spin Oscillator models. 
    \item Begin by giving a brief overview of TLS-HO - use short examples e.g. biological systems, which you will later expand on. \textcolor{red}{Find [10] references.}
    \item Brief overview of Quantum Resources (entanglement and coherence).\textcolor{red}{Find [5] references.}
    \item Very short summary on structure of essay. "We begin by..."
\end{enumerate}


\section{TLS-HO Model}
\begin{enumerate}
    \item Chronologically introduce Spin-Oscillator, from JC Hamiltonian up to status quo. "The inception of...up till present, being used in...".
    \item Show that the system is very relevant - go through all examples of systems, past to present.
    \item Open problems of Spin oscillator. 
    \subitem (i) \textcolor{red}{Find [2-3] references.}
    \subitem (ii) The problem with JC model is that beyond the given approximations, the model begins to fail. \textcolor{red}{Find [2-3] references.}
    \subitem (iii) When you start introducing more than one TLS, model breaks. CRITICALITY HERE.
    \item At the end, connect the TLS-HO model to section 4 i.e. why we need to consider q resources.
\end{enumerate}

\section{Quantum Resources: Entanglement and Coherence}

\begin{enumerate}
    \item Talk about what Quantum resources are, and what field/s they are used in. \textcolor{red}{Find [2] references.}
    \item Talk about the need to look at quantum resources. 
    \item Mention the close relation between coherence and entanglement. basis dependence, etc. 
\end{enumerate}

\subsection{Entanglement}
\begin{enumerate}
    \item Chronologically introduce Entanglement from past to status quo.
    \item Look at different measures of entanglement. So far, EoF and Concurrence, Renyi, REE, robustness, VNE.
\end{enumerate}

\subsection{Coherence}
\begin{enumerate}
    \item Chronologically introduce Coherence from past to status quo.
    \item Look at different measures of entanglement. So far, REC, Norm 
    \item Mention measures vs monotones.
\end{enumerate}

\section{Application to our System}
\begin{enumerate}
    \item Why look at this? explain. 
    \item Cover the use of Quantum Resources within Spin Oscillator models. \textcolor{red}{Find [5] references.}
\end{enumerate}

\section{Conclusion}
\begin{enumerate}
    \item Status quo summary of Spin-Oscillators.
    \item Status quo summary of Quantum Resources. 
    \item Conclusions about Spin Oscillators - their relevance, their open problems.
    \item Conclusions about Quantum Resources - their relevance, their open problems. 
\end{enumerate}

\end{document}