\documentclass{article}
\usepackage{hyperref}
\usepackage{indentfirst}
\begin{document}

\section*{Week 3 Summary}

\vspace{0.5cm}

\textbf{Analytical objectives.} I successfully found the reduced density matrix of the general state. Upon review, it is \textbf{critical} to include information about time dependence, as well as writing out the elements in full instead of only in matrix form. 

However, for the density matrix in terms of the eigenstates, I did not correctly compute the reduced density matrix. Instead of tracing out the eigenstates (which has no physical meaning), I should have traced out the subsystems. I need to start considering what the maths means in terms of the Physics. 

Lastly, whilst I did correctly find that the Von Neumann entropy is 0 for pure states, that is not what the reference asked. I need to consider the Von Neumann entropy for the reduced states! I did not calculate the relative entropy of entanglement.

\vspace{0.5cm}

\textbf{Reading objectives.} Whilst I found a good few references, I did not have time to read it, and they shall be read in week 6. 

\vspace{0.5cm}

\textbf{Reflection and aims for Week 6.} I need to ensure that I think about the Physics of systems, as this is what really matters. Furthermore, I need to think more carefully about bases, and this can be done by writing out elements in full instead of only in matrix form. 
For week 6, I will need to correctly compute the reduced density matrices of the composite system, find the given Von Neumann entropy, and also the Relative Entropy of Entanglement. 

\end{document}